Effects of bariatric surger and weight loss on resting-state functional connectivity

### 2021-01-14 manuscript/draft_rsfmri.Rmd
add pause option to inspect contrasts

## Interaction effect of intervention and time (preregistered analysis)

>>>>

```{r "Descriptive results", include=FALSE}
m = lme4::lmer(BMI ~ group*visit + (visit+1|subj.ID), data=final)
summary(m)
confint(m, method='profile', oldNames=FALSE)
```
## Interaction effect of intervention and time (preregistered analysis)

### 2021-01-14 manuscript/intro_rsfmri.Rmd
add pause option to inspect contrasts

<!-- Reward network -->
Little is known about the potential beneficial effects of bariatric surgery on brain function in the obese population. Thus, one recently emerging research focus is how brain metabolism and functional connectivity changes in response to surgery, in particular with regard to hedonic motivations for food, which play a fundamental role in weight relapse.
The reward network comprising the ventromedial prefrontal cortex (vmPFC), the striatum (STR) but also the anterior insula (antINS) has been linked to food valuation processes in decision-making in lean individuals [@Bartra_2013; @Hare_2011; @Hutcherson_2012; @Schmidt_2018; @Wiemerslage_2016]. These regions also seem to be altered after bariatric surgery [@Lips_2014; @Hogenkamp_2016; @Garcia_2012]. <!-- mehr zu Zitationen -->
<!-- Normalization of connectivity --> Obese individuals exhibited increased connectivity between frontal and mesolimbic regions and weaker connectivity within regions of the mesolimbic system (encompassing limbic and striatal regions). But these differences seemed to normalize, as trends reversed when looking at the resting state connectivity after compared to before the surgery [@Duan_2020]. Resting state activitiy increased in subcortical regions, such as the insula and striatum<!-- specifically putamen --> [@Wiemerslage_2016]. 
<!-- mechanism reward and appetite, overeating --> Interestingly, patients report changes in food preferences and eating behavior after the surgery that may influence weight loss beyond malabsorption of nutrients and restricted food ingestion. Those psychophysiological and behavioral effects are presumably related to post-surgical changes in visceral sensory perceptions and endocrinological signaling. Corresponding information is processed by the fronto-mesolimbic system and affects appetite and reward signalling which may influence weight regulation [@Mulla_2017; @Nudel_2019].
<!-- results in lean -->

>>>>

<!-- Reward network -->
Little is known about the potential beneficial effects of bariatric surgery on brain function in the obese population. Thus, one recently emerging research focus is how brain metabolism and functional connectivity changes in response to surgery, in particular with regard to hedonic motivations for food, which play a fundamental role in weight relapse.
The reward network comprising the ventromedial prefrontal cortex (vmPFC), the striatum (STR) but also the anterior insula (antINS) has been linked to food valuation processes in decision-making in lean individuals [@Bartra_2013; @Hare_2011; @Hutcherson_2012; @Schmidt_2018; @Wiemerslage_2016]. These regions also seem to be altered after bariatric surgery [@Lips_2014; @Hogenkamp_2016; @Garcia_2012]. <!-- mehr zu Zitationen -->
<!-- Normalization of connectivity --> Obese individuals exhibited increased connectivity between frontal and mesolimbic regions and weaker connectivity within regions of the mesolimbic system (encompassing limbic and striatal regions). These abnormalities in resting-state connectivity in obese compared to normal-weight individuals seemed to normalize, as trends reversed after compared to before the surgery [@Duan_2020]. Resting state activitiy increased in subcortical regions, such as the insula and striatum<!-- specifically putamen --> [@Wiemerslage_2016]. 
<!-- mechanism reward and appetite, overeating --> Interestingly, patients report changes in food preferences and eating behavior after the surgery that may influence weight loss beyond malabsorption of nutrients and restricted food ingestion. Those psychophysiological and behavioral effects are presumably related to post-surgical changes in visceral sensory perceptions and endocrinological signaling. Corresponding information is processed by the fronto-mesolimbic system and affects appetite and reward signalling which may influence weight regulation [@Mulla_2017; @Nudel_2019].
<!-- results in lean -->
